\pkg{casebase}: An Alternative Framework For Survival Analysis and Comparison of Event Rates

### 2022-06-07 analysis/paper/bhatnagar-turgeon-islam-hanley-saarela.Rmd
reorder terms in formula

```{r, echo = TRUE, eval = FALSE}
fitSmoothHazard(DeadOfPrCa ~ as.integer(Follow.Up.Time >= t0) :
                    I(Follow.Up.Time - t0) : ScrArm,
                data = ERSPC)
```

\noindent Here, we use the binary variable `as.integer(Follow.Up.Time >= t0)` in order to write the two cases of our formula above in a more compact way. We also use the function `I()`, which allows us to specify new variables within the formula using normal `R` code. This is required, as otherwise the symbol `-` would be interpreted as a formula operator. Finally, we use the operator `:` instead of `*` in order to only include the interaction term, not the main effects.

>>>>

```{r, echo = TRUE, eval = FALSE}
fitSmoothHazard(DeadOfPrCa ~ as.integer(Follow.Up.Time >= t0) :
                    ScrArm : I(Follow.Up.Time - t0),
                data = ERSPC)
```

\noindent Here, we use the binary variable `as.integer(Follow.Up.Time >= t0)` in order to write the two cases of our formula above in a more compact way. We also use the function `I()`, which allows us to specify new variables within the formula using normal `R` code. This is required, as otherwise the symbol `-` would be interpreted as a formula operator. Finally, the term `ScrArm : I(Follow.Up.Time - t0)` represents the product $Z (t - t_0)$ in the equation above. We use the operator `:` instead of `*` in order to only include the interaction term, not the main effects.

### 2022-06-07 analysis/paper/bhatnagar-turgeon-islam-hanley-saarela.tex
reorder terms in formula

\begin{Schunk}
\begin{Sinput}
fitSmoothHazard(DeadOfPrCa ~ as.integer(Follow.Up.Time >= t0) :
                    I(Follow.Up.Time - t0) : ScrArm,
                data = ERSPC)
\end{Sinput}
\end{Schunk}

\noindent Here, we use the binary variable
\texttt{as.integer(Follow.Up.Time\ \textgreater{}=\ t0)} in order to
write the two cases of our formula above in a more compact way. We also
use the function \texttt{I()}, which allows us to specify new variables
within the formula using normal \texttt{R} code. This is required, as
otherwise the symbol \texttt{-} would be interpreted as a formula
operator. Finally, we use the operator \texttt{:} instead of \texttt{*}
in order to only include the interaction term, not the main effects.

>>>>

\begin{Schunk}
\begin{Sinput}
fitSmoothHazard(DeadOfPrCa ~ as.integer(Follow.Up.Time >= t0) :
                    ScrArm : I(Follow.Up.Time - t0),
                data = ERSPC)
\end{Sinput}
\end{Schunk}

\noindent Here, we use the binary variable
\texttt{as.integer(Follow.Up.Time\ \textgreater{}=\ t0)} in order to
write the two cases of our formula above in a more compact way. We also
use the function \texttt{I()}, which allows us to specify new variables
within the formula using normal \texttt{R} code. This is required, as
otherwise the symbol \texttt{-} would be interpreted as a formula
operator. Finally, the term \texttt{ScrArm\ :\ I(Follow.Up.Time\ -\ t0)}
represents the product \(Z (t - t_0)\) in the equation above. We use the
operator \texttt{:} instead of \texttt{*} in order to only include the
interaction term, not the main effects.
